Predicting Water Treatment Plant Chemical Doses

### 2025-12-10 Presentation DSCI445.Rmd
Fixed tree slides

```{r, fig.width=7, fig.height=3.8}
set.seed(445)

@@

**Note - make a cleaner table!**

```{r, fig.width=6.5, fig.height=3.4}
set.seed(445)

@@

model_metrics = predictions %>%
  metrics(truth = FeCl_dose, estimate = .pred) # Change target variable here

print(model_metrics)

vip(fit_rf, bar = TRUE) +
  theme_minimal(base_size = 14) +
  labs(title = "Top Feature Importances")

>>>>

```{r, fig.width=5, fig.height=2.5}
set.seed(445)

@@

```{r, fig.width=5, fig.height=2.1}
set.seed(445)

@@

model_metrics = predictions %>%
  metrics(truth = FeCl_dose, estimate = .pred) # Change target variable here
rmse = model_metrics$.estimate[1]
r_squared = model_metrics$.estimate[2]
mae = model_metrics$.estimate[3]

vip(fit_rf, num_features = 20) +
  geom_col(color = "black", fill = "coral") +
  labs(
    title = "Feature Importance (Random Forest)",
    x = "Importance",
    y = "Feature"
  ) +
  theme_minimal(base_size = 9)
